Bayesian Sparsification of $\cplx$-valued networks

### 2019-12-02 paper/paper.tex
path fixes
added references for cplx network overview

Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
of $\cplx$-argument, \citep{adali_complex-valued_2011}. The rules it defines satisfy intuitive
linearity, product and chain rules, and respect complex conjugation, but most importantly the
$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
as a basis for $\cplx$ version of backpropagation in \citep{benvenuto_complex_1992} and
\citep{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
%
\todo{read on holomorphic nets}

>>>>

Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
of $\cplx$-argument, \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
product and chain rules, respects complex conjugation and linearity, but most importantly the
$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
as a basis for $\cplx$ version of backpropagation in \citep{benvenuto_complex_1992} and
\citep{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
%
\todo{read on holomorphic nets}
